Paper on the carbonate chemistry at Ny-Ålesund

### 2020-03-11 paper.Rmd
more figures in paper.Rmd

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
#library(robfilter)
library(seacarb)
library(gridExtra)
#library(reshape2)
library(lubridate)
#library(lmtest)
#library(grid)
library(viridis)
#library(dygraphs)
require("knitr")
library("lmodel2")
#library(captioner)
#library(xts)
#library(seismicRoll)
#library(scales)
knitr::opts_chunk$set(echo = TRUE)

@@

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

@@

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

# Add the flag location: some samples have been collected at the peer. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1,0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

# Keep only flag = 2 for at/ct analysis 
# Keep only flag = 2 for pH durafet and seaFET.
d <- d%>%
  dplyr::mutate(ct= replace(ct, qflag_ct != 2, NA),
                at= replace(at, qflag_at != 2, NA),
                pH_s_seafet= replace(pH_s_seafet, qflag_pH_s_seafet != 2, NA),
                pH_s_durafet= replace(pH_s_durafet, qflag_pH_s_durafet != 2, NA))

# Mercury chloride correction (Dickson et al. 2007, SOP3a)
# AT
d$at <- d$at * 1.0002
#CT
d$ct <- d$ct * 1.0002

# Fill "at/ct" to all line with same day.
at_ct_mean <- d %>% 
  group_by(datetime)%>%
  dplyr::summarize(at_mean = mean(at, na.rm = T),
                   ct_mean = mean(ct, na.rm = T),
                   at_sd = sd(at, na.rm = T), 
                   ct_sd = sd(ct, na.rm = T)
                   )
#at_ct_mean <- at_ct_mean%>%filter(!is.na(at_mean))
#write.table(file= paste0(path, "fb_data/at_ct_mean.txt"), at_ct_mean)
d <- left_join(d, at_ct_mean, by='datetime')
# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule=2)
names(CTinterp) <- c("datetime", "ct_mean_interp")
CTinterp <- as.data.frame(CTinterp)
d$ct_mean_interp <- CTinterp$ct_mean_interp

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
            temp = mean(temp_field, na.rm = T),
            at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019

# discrete_steffen <- discrete[c(21:72),1:4]
# write.table( discrete_steffen,"../fb_data/DiscreteTA_for_steffen.txt", sep= ",", dec=".", row.names = FALSE)

carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
discrete$phcalc<- carb$pH
discrete$pco2calc<- carb$pCO2
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
```

```{r Combine discrete and continous data, echo=FALSE}
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
# remove the drop_na() because of seafet/durafet line with na
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# ct
# closest <- which.closest(discrete$datetime, d$datetime) # closest date and time
# discrete$closest_datetime <- d$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ct, qflag_ct) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pH calculated
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, phcalc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pCO2
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

save(file= paste0(path, "fb_data/d_all.rds"), d_all)

## bind the voltages and deployment ##

# Duplicate datetime in closest_datetime to do the left_join
d_all$closest_datetime <- d_all$datetime
discrete <- left_join(discrete, d_all%>%dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
```

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
h3{ /* Header 3 */
  font-size: 22px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h4{ /* Header 4 */
  font-size: 18px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h5{ /* Header 5 */
  font-size: 16px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
</style>

# {.tabset .tabset-fade .tabset-pills}

## Infos

### **Introduction**
<div style="text-align: justify">  
The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory. It comprises two components: (1) continuous real-time measurements and (2) discrete measurements. The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.

### **AWIPEV Underwater Observatory**
<div style="text-align: justify">  
The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems. The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured. Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP for continuous measurements of currents and waves. Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations. The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter. During this time, the system is remotely controlled and maintained from Germany. All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed. The processed data are open access and available at http://codm.hzg.de/codm.

<div style="text-align:center" markdown="1">
  <img  src="./Images/Container.png" width="200" height="200">
  <img  src="./Images/Intake.png" width="200" height="200">
  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
</div>

### **Continuous and semi-continuous measurements**
<div style="text-align: justify">  
The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015. Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry. Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit. The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading. The sensor is the first instrument in the measuring loop; data are logged every minute. This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.

Since February 2016, total alkalinity (AT) is measured every 90 min with a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through system). Fifty ml of seawater is filtered (0.2 um) using a Contros-Kongsberg cross-flow filter and then acidified using dilute hydrochloric acid (0.1 N). CO~2~ is then flushed out (open-cell titration) and the final pH measured by means of an indicator dye (bromocresol green) and visible absorption spectrometry. Together with salinity and temperature at the time of measurement, the pH reading is used to calculate AT. According to the manufacturer, the measuring range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25 umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).

In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been added to the UWO. This new sensor continuously measures pH at 11 m using an ISFET (Ion Sensitive Field Effect Transistor). According to the manufacturer, the measuring range is between 6.5 and 9 pH units, initial accuracy is 0.02 pH units and precision is 0.004 pH units. Operating salinity and temperature range are 20 to 40 PSU and 0 to 50°C respectively.

In August 2017, a Durafet III pH electrode connected to a UDA2128 Analyser (Honeywell) was also implemented to the Ferrybox flow-through system. This electrode continuously measures pH, in the Ferrybox, through an ISFET. According to the manufacturer, the measuring range is between 0 and 14 pH units.

### **Data availability**
TO DO: add here an horizontal bar plot showing the percent availability of the data

## Whole time series
```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#SAL
sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
  dplyr::filter(sal_fb >28)
sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
      dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# TEMP Ferrybox SBE45
temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
      dyAxis("y", valueRange = c(-2.5, 10)) %>%
      dyLegend(show = "follow")   %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# TEMP insitu SBE38
temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
      dyAxis("y", valueRange = c(-2.8, 10)) %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyLegend(show = "follow")   %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# PCO2 
#+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
      dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyAxis("y",valueRange = c(8, 8.8)) %>%
    dyLegend(show = "follow")   %>%
    dyRangeSelector(height = 30, dateWindow= NULL) 
# SEAFET 
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyAxis("y",valueRange = c(7.45, 8.8)) %>%
    dyLegend(show = "follow")   %>%
    dyRangeSelector(height = 30, dateWindow= NULL) 
# TA
# to create periods according to TA deployments
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
#library(robfilter)
library(seacarb)
library(gridExtra)
#library(reshape2)
library(lubridate)
#library(lmtest)
#library(grid)
library(viridis)
#library(dygraphs)
require("knitr")
library("lmodel2")
#library(captioner)
#library(xts)
#library(seismicRoll)
library(scales)
knitr::opts_chunk$set(echo = TRUE)

@@

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        #aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

@@

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tibble(
  readRDS(file = paste0(path, "fb_data/d_all.rds"))
) %>%
  filter(sal_fb > 28) # remove salinity data lower than 28
```

## Whole time series
```{r whole time series, fig.width=10, fig.height=15, echo=FALSE, message= FALSE}
size_point <- 1 # size of data points

#SAL SBE45
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox? SBE45",x="", y="Salinity") +
  #coord_fixed() +
  Mytheme(size_labs = 8)

# TEMP in situ SBE38
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Temperature SBE38",x="", y="In situ temperature (°C)") +
  #coord_fixed() +
  Mytheme(size_labs = 8)

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_contros), 
             colour="black", na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2calc), colour="blue", na.rm=TRUE, size=size_point) + 
  labs(title="CO2 partial pressure",x="", y="pCO2 (uatm)") +
  #coord_fixed() +
  Mytheme(size_labs = 8)

# SEAFET pH
ts_pH <- d_all %>%
  ggplot(aes(x = datetime, y = pHint_tot_sf), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="In situ pH",x="", y="pCO2 (uatm)") +
  #coord_fixed() +
  Mytheme(size_labs = 8)

# TA
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Total alkalinity calculated from salinity", x="", y="AT (umol/kg)") +
  #coord_fixed() +
  Mytheme(size_labs = 8)

g <- cowplot::plot_grid(ts_sal, ts_temp, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
print(g)
```

```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
temp_sal <- d_all %>%
  ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
  #scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
  coord_fixed() +
  Mytheme(size_labs = 8) #+
  #theme(axis.text.x=element_blank())
#  +annotation_custom(grob_A)
print(temp_sal)
